Title of Paper

### 2017-02-17 paper.tex
fix labels in graph, sort
add first conclusions

\subsection{Code Generation}
Code generation is handled by the python package \texttt{loo.py}~\cite{kloeckner_loopy_2014}, which provides an interface to OpenCL allowing for unit testing and changes of program structure, e.g. data ordering, vectorization, threading patterns etc.
Additionally, \texttt{loo.py} allows for code generation for multiple languages, including (non-vectorized) C, CUDA, and Intel's ISPC compiler, which targets SIMD vectorization on the CPU and MIC.
This is a direction that may be explored in the future to compare the speedups of the various compilers.

@@

\begin{table}[htb]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$E_{R_{i}^{\prime}}$} & \multicolumn{1}{c}{$E_{R_{i}^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R_{i}}$} & \multicolumn{1}{c}{$\text{P}_{\text{min}}^{*}\si{\percent}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[C_k]}{\text{d}t}}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[T]}{\text{d}t}}$} \\
\midrule
\multicolumn{1}{c}{\ce{H2}\slash~\ce{CO}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 4.66e6 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{c}{GRI-Mech.~3.0}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 2.67e04 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{c}{USC-Mech II}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 4.12e02 & 7.92e00 & 3.22e03 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
\todo[inline]{i-pentanol validation still running}
}
\label{T:error}
\end{table}

@@

\section{Conclusions}
%

@@

\noindent\textbf{Page Limits:} The total length of the paper including references should be limited to 6 pages.

>>>>

\subsection{Code Generation}
Code generation is handled by the python package \texttt{loo.py}~\cite{kloeckner_loopy_2014}, which provides an interface to OpenCL allowing for unit testing and changes of program structure, e.g. data ordering, vectorization, threading patterns etc.

@@

\begin{table}[htb]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{l}{Model} & \multicolumn{1}{c}{$E_{R_{i}^{\prime}}$} & \multicolumn{1}{c}{$E_{R_{i}^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R_{i}}$} & \multicolumn{1}{c}{$\text{P}_{\text{min}}^{*}\si{\percent}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[C_k]}{\text{d}t}}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[T]}{\text{d}t}}$} \\
\midrule
\multicolumn{1}{l}{\ce{H2}\slash~\ce{CO}\cite{Burke:2011fh}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 4.66e6 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{l}{GRI-Mech.~3.0\cite{smith_gri-mech_30}}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 2.67e04 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{l}{USC-Mech II\cite{Wang:2007}}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 4.12e02 & 7.92e00 & 3.22e03 \\
\multicolumn{1}{l}{\ce{IC5H11OH}\cite{Sarathy:2013jr}} & -1 &  -1 & -1 & -1 & -1 & -1 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
\todo[inline]{i-pentanol validation still running}
}
\label{T:error}
\end{table}

@@

\section{Conclusions}
In this work, a shallow SIMD-vectorized chemical source term evaluation OpenCL code generator was developed and validated against Cantera~\cite{Cantera} for a wide range of chemical kinetic models~\cite{Burke:2011fh,smith_gri-mech_30,Wang:2007,Sarathy:2013jr}.
Significant speedups of up to \SI{2.42}{$\times$} over a baseline SIMT-vectorized code were observed.
Two data-ordering schemes were investigated, showing a clear performance benefit for use of the ``C'' (row-major) ordering for the shallow vectorized code.
Further, this study suggests that a deep SIMD-vectorized code---currently under development---may see even greater accelerations due to expected increases in cache-hit rates.
Larger vector widths were found to provide accelerations for the smaller models studied, but performance was similar over all vector widths tested for the largest models tested.
Finally, the strong parallel scaling efficiency was examined for the shallow vectorized code; the larger models exhibited higher scaling efficiency, possibly due to failure of the \ce{H2}\slash\ce{CO} model to saturate the CPU throughput.
Future extensions of this work will include development of a SIMD\slash SIMT-accelerated sparse-analytical Jacobian code targeted at CPUs, GPUs and MICs.

@@
